### 2018-12-27 Chapitres/ExtractionMotifs/SynNoeudClust.tex
Introd_Gen

				\begin{landscape}
								\begin{table}
									\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
										\hline
										\multirow{2}{*}[-25pt]{Article}  & \multicolumn{4}{c|}{Graphe en entrée} & \multicolumn{2}{c|}{Compression} & \multicolumn{2}{c|}{Structure en sortie}  & \multirow{2}{*}[-25pt]{Graphe de test} & \multirow{2}{*}[-25pt]{Résultat}  \\ \cline{2-11}
				& \rotatebox[origin=c]{90}{ Orienté }  & \rotatebox[origin=c]{90}{ Non orienté } & \rotatebox[origin=c]{90}{ Statique } & \rotatebox[origin=c]{90}{ Dynamique } & \rotatebox[origin=c]{90}{ Avec perte } & \rotatebox[origin=c]{90}{ Sans perte } & \rotatebox[origin=c]{90}{ Succincte } & \rotatebox[origin=c]{90}{ Structurelle }  & & \\ \hline				%%%%%%Fin du header

										\hline VoG \citep{koutra2015summarizing} & \xmark & \cmark & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark  &

@@

										\hline VoG-Overlapp \citep{liu2015empirical}& \xmark & \cmark & \cmark & \xmark & \xmark &\cmark & \cmark & \xmark  &

@@

    \end{itemize}
  \end{minipage}	
										 & 25\%	\\
										\hline TimeCrunch \citep{shah2015timecrunch}& \xmark & \cmark & \cmark & \xmark & \xmark &\cmark & \cmark & \xmark &

@@

    \end{itemize}
  \end{minipage}											
										&74\%	\\
										\hline CanDenSe \citep{liu2018reducing}&     \xmark & \cmark & \xmark & \cmark & \xmark  &\cmark & \cmark & \cmark &
\begin{minipage}[t]{0.3\textwidth}
	Enron
    \begin{itemize}
    \item 80 milles nœuds
    \item 288 milles liens\\

>>>>

				\begin{landscape}
								\begin{table}
									\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
										\hline
										& \multirow{2}{*}[-25pt]{Article}  & \multicolumn{4}{c|}{Graphe en entrée} & \multicolumn{2}{c|}{Compression} & \multicolumn{2}{c|}{Structure en sortie}  & \multirow{2}{*}[-25pt]{Graphe de test} & \multirow{2}{*}[-25pt]{Résultat}  \\ \cline{2-11}
				& \rotatebox[origin=c]{90}{ Orienté }  & \rotatebox[origin=c]{90}{ Non orienté } & \rotatebox[origin=c]{90}{ Statique } & \rotatebox[origin=c]{90}{ Dynamique } & \rotatebox[origin=c]{90}{ Avec perte } & \rotatebox[origin=c]{90}{ Sans perte } & \rotatebox[origin=c]{90}{ Succincte } & \rotatebox[origin=c]{90}{ Structurelle }  & & \\ \hline				%%%%%%Fin du header

										 \rotatebox[origin=c]{90} \multirow{4}{*}[-25pt]{Basé vocabulaire en utilisant les méthodes de clustering} & VoG \citep{koutra2015summarizing} & \xmark & \cmark & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark  &

@@

										 & VoG-Overlapp \citep{liu2015empirical}& \xmark & \cmark & \cmark & \xmark & \xmark &\cmark & \cmark & \xmark  &

@@

    \end{itemize}
  \end{minipage}	
										 & 25\%	\\
										 & TimeCrunch \citep{shah2015timecrunch}& \xmark & \cmark & \cmark & \xmark & \xmark &\cmark & \cmark & \xmark &

@@

    \end{itemize}
  \end{minipage}											
										&74\%	\\
										 & CanDenSe \citep{liu2018reducing}&     \xmark & \cmark & \xmark & \cmark & \xmark  &\cmark & \cmark & \cmark &
\begin{minipage}[t]{0.3\textwidth}
	Enron
    \begin{itemize}
    \item 80 milles nœuds
    \item 288 milles liens\\
